Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-12-11 scagnostics.Rmd
Updated smoothing plot.

```{r spiralScagSmoothing, fig.cap="Comparing the traces of the three scagnostics indices when smoothing the index values, either by averaging over the index value after jittering the projection by some angle $\\epsilon$ (left) or after jittering the projected datapoints with some amount $\\beta$ (right). While the behaviour can be somewhat improved, sharp jumps can be observed in all settings considered."}

@@

if(!file.exists("cache/spiralScagSmoothing.rda")){
  scagSmooth <- getScagSmooth(spiral1000, as.list(t2full))
  scagSmoothMelt <- gather(scagSmooth, variable, value, -t, -method, -alpha)
  save(scagSmooth, scagSmoothMelt, file = "cache/spiralScagSmoothing.rda")
} else {
  load("cache/spiralScagSmoothing.rda")
}

ggplot(scagSmoothMelt, aes(x=t, y=value)) +
  geom_line(aes(color=factor(alpha))) + 
  facet_wrap(variable~method, ncol=2, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE))

>>>>

\textcolor{red}{I fixed the y axis to be between 0 and 1, which highlights that indeed we get much smoother behaviour, on the other hand theres still large relative jumps observed in all traces, and a smaller y axis scale may be preferred to show this more clearely.}

```{r spiralScagSmoothing, fig.cap="Comparing the traces of the scagnostics indices skinny and stringy when smoothing the index values, either by averaging over the index value after jittering the projection by some angle $\\epsilon$ (full line) or after jittering the projected datapoints with some amount $\\beta$ (dashed line). While the behaviour can be somewhat improved, sharp jumps can be observed in all settings considered."}

@@

if(!file.exists("cache/spiralScagSmoothing.rda")){
  scagSmooth <- getScagSmooth(spiral1000, as.list(t1full))
  scagSmoothMelt <- gather(scagSmooth, variable, value, -t, -method, -alpha)
  save(scagSmooth, scagSmoothMelt, file = "cache/spiralScagSmoothing.rda")
} else {
  load("cache/spiralScagSmoothing.rda")
}

scagSmoothMelt <- scagSmoothMelt %>%
  filter(variable != "convex") %>%
  mutate(method = factor(method, levels = c("jitterAngle", "jitterPoints")))
ggplot(scagSmoothMelt, aes(x=t, y=value)) +
  geom_line(aes(linetype=factor(method))) + 
  theme(legend.position="none") +
  ylim(0,1) +
  facet_grid(alpha~variable) +
  xlab("Sequence of projections (t)") +
  ylab("PPI value")
